---
title: "Landslide Prediction"
output:
  pdf_document: default
  html_document: default
---
## By Ghozian Islam Karami
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, error=FALSE)
knitr::opts_knit$set(root.dir = "D:/Tutorial/Geosoftware Tutorial/R/Landslide prediction machine learning/Sesi 2/Tugas/02_data latihan/Longsor R")
#setwd("D:/Tutorial/Geosoftware Tutorial/R/Landslide prediction machine learning/Sesi 2/Tugas/02_data latihan/Longsor R")

```

### Open Library and set directory
```{r Library}
library(raster)
library(rgdal)
library(sp)
library(dplyr)
library(DMwR)
library(caret)
library(snow)
library(rgeos)
library(maptools)
library(gdalUtils)
```

## Create non-landslide datapoints sample from slope data

```{r non lanslide}
#load slope .tif
slope <- raster("slope.tif")
#create vector classified
# slope with 0-10 classified as 1 (no landslide is accuired), rest is NA (it will not used)
reclass_df <- c(0, 10, 1, 10, Inf, NA)
#convert to matrix
reclass_m <- matrix(reclass_df, ncol = 3, byrow = TRUE)
reclass_m 
#reclasify
slope_classified <- reclassify(slope, reclass_m)
plot(slope_classified)

#write raster to tif (Unfortunately, rasterToPolygon was showing error)
#writeRaster(slope_classified, file="slope_class", format="GTiff", overwrite=TRUE)
#convert the raster to polygon in QGIS
#import the shapefile processed by QGIS
poly_nols <- readOGR("no_ls_poly_class.shp")

#create random sample in slope polygon area (only no landslide / 1)
no.ls<-spsample(poly_nols,n=100,"random")
#convert coordinate to same as slope
no.ls <- spTransform(no.ls, CRS = CRS(proj4string(slope)))
crs(no.ls)
class(no.ls)
#convert to spatial point dataframe
no.ls.spdf <- as(no.ls,"SpatialPointsDataFrame")
#convert to  dataframe (just coordinates)
df <- as.data.frame(no.ls.spdf@coords)
class(df)

#Export to csv
#write.csv(df, file="no_ls.csv")

```


## Raster Preparation for creating a merge raster
```{r Raster Preparation}
#create merged raster (mozaic raster)

#merged raster
a <- c('slope.tif', 'ndvi.tif', 'landuse2.tif', 'elevasi2.tif','Curvature.tif')
e <- extent(slope)
template <- raster(e)
#so the raster will be the same extent?? #try to do this code with insar data
proj4string(template) <- CRS('+init=epsg:23037')
writeRaster(template, file="merged.tif", format="GTiff", overwrite=TRUE)

mosaic_rasters(gdalfile=a,dst_dataset="merged.tif",of="GTiff",separate=TRUE)
```

## Raw CSV data training and data test preparation
### Raw csv = input data that has ls and no ls points, so we need Ls data to be combined with LS data
### this can be done by using QGIS
1. Input Landslide data from panitia (add a new field, fill with "2" for the class)
2. Input csv no ls data and fill "1" for class
3. combine the data into input.shp

```{r}
rasstack=stack("merged.tif")
point=readOGR("input.shp")
#extract raster value from point 
head(point)
#how to delete column from spatial point dataframe file
point <- point[,-(4:10)]
rasvalue=extract(rasstack,point)
head(rasvalue)
combined=cbind(point,rasvalue)
head(combined)
head(rasvalue)
head(point)

#change column name
colnames(combined@data)[1] = "class"
colnames(combined@data)[4] = "B1"
colnames(combined@data)[5] = "B2"
colnames(combined@data)[6] = "B3"
colnames(combined@data)[7] = "B4"
colnames(combined@data)[8] = "B5"


#look at the data count
combined@data %>%
  group_by(class) %>%
  summarise(
    count = n()
  )
combined

#change to dataframe?
val=combined@data
val <- na.omit(val)
head(val)
class(val)


#randomize the data row
val=val[sample(nrow(val)),]
val$class = as.factor(val$class)
class(val)
head(val)


```

## Build a model using Random Forest Classification Algorithm

```{r}

N_FILES=80 #jumlah data
SPLT=0.8 #80% train
b = floor(SPLT*N_FILES)
train = val[1:b,]
test = val[(b+1):N_FILES,]
#random forest using caret
modFit_rf <- caret::train(class ~ B1+B2+B3+B4+B5, method = "rf", data=train)

validation_result<-predict(modFit_rf,newdata=test)
result_comparison<-cbind(as.numeric(as.character(validation_result)),test[,1]) # class on column 1
preds<-result_comparison[,1]
y<-result_comparison[,2]

#check validation result and accuracy
confmat <- confusionMatrix(as.factor(y),as.factor(preds), positive='2')
confmat
library(pROC)
kurva_roc<-roc(preds, y, levels=c("1", "2"))
plot(kurva_roc)
img_subset <- brick("merged.tif")
names(img_subset) <- c(paste0("B", 1:5, coll = ""))

#image prediction and write image
beginCluster()
preds_rf <- clusterR(img_subset, raster::predict, args = list(model = modFit_rf))
endCluster()
plot(preds_rf)
writeRaster(preds_rf, "rf_result_ls_pred", format = "GTiff", overwrite=TRUE)
gc()


```

