---
title: "Udemy Training"
output: html_notebook
---


### statistics function 
```{r}

lvl <- c(8, 10, 10, 1, 10)
sum(lvl)
mean(lvl)
median(lvl)
length(lvl)
sd(lvl)
round(lvl)

```

### slicing and indexing a vector
```{r}
lvl["c"]
lvl[3]
lvl[c(3, 5, 7, 1)]
lvl[lvl > 5]
```

### Function
```{r}
#Creating a function
draw <- function(){
  deck <- c("Head", "Tail")
  hand <- sample(deck, size=2, replace = T, prob = c(0.3, 0.7))
  print(hand)
}

draw()

```

### Matrix
- Creating matrix
- Indexinf Matrix
- matrix Arithmetic
```{r}

#to bend the object.to.transform into a two dimensional object with n rows and m columns
#so the a is converted into matrix class, before dim is numeric class.. but the type is still "double"
a <- seq(10, 90, by = 10)
dim(a) <- c(3,3)
a

#create a hypercube 
dim(a) <- c(1,3,3)

#use dim (cannot be recycle)
b <- c("dark", "dark", "dark", "dark", "light", "light", "king", "queen", "pawn", "test")
dim(b) <- c(5,2)

#use matrix
amatrix <- matrix(b, nrow = 8, ncol = 2)
amatrix

#use cbind
abind <- cbind(amatrix, amatrix)
abind

#how to assign row and col names
colnames(abind) <- c("column1", "column2", "column3", "column4")
rownames(abind) <- c("row1", "row2", "row3", "row4", "row1", "row2", "row3", "row4")

#how to create a matrix in single code
gdp <- matrix(c(3, 4, 5, 1, 6, 7, 8, 10, 11),
              nrow = 3, byrow = TRUE,
              dimnames = list(c("de", "usa", "ind"), c("2014", "2013", "2010"
                                                       )))
gdp
#to export dataframe
write.csv(gdp, "C:\\Users\\ghozi\\Desktop\\MyData.csv")


#Indexing a matrix #same as indexing and slicing a vector, but with [row , column]
abind
abind[2, 2]
abind[2, ]
abind[, 2]
abind[c(1, 3, 5)]
abind[c(1, 3, 5), ]
abind["row3", ]
abind[ , "column2" ]


#Matrix Arithmetic
matrixb <- matrix(c(1:20), nrow = 6, ncol = 4)
matrixb
colSums(matrixb)
colMeans(matrixb)
rowSums(matrixb)
rowMeans(matrixb)

#matrix multiplication using %*%
#Note that first ncolumn is needed to be same as second nrow 

matrixc <- matrix(c(1:20), nrow = 4, ncol = 6)
m.multiplied <- (matrixb %*% matrixc)
m.multiplied
```

#Creating a factor
```{r}
#Creating a factor (ordinal data)

marital.status <- c("Married", "Married", "Single", "Married", "Divorced", "Widowed", "Divorced")

#to know the type of the data
str(marital.status)

#convert into factor variable

marital.factor <- factor(marital.status)
str(marital.factor) 
#notice the variable are converted into integrer, ordered alpahabeticaly

#how to order based on the levels
ordered.factor <- factor(marital.status, ordered = TRUE, 
                         levels = c("Single", "Married", "Divorced", "Widowed"))
str(ordered.factor)

```

#Using List
```{r}
#Using List

my.book <- list("1984", "George", "1949", 
                list(c(1:8), c(1:10), c(1:6), "Newspeak"))
my.book
str(my.book)


#Naming A List

my.book <- list(Name = "1984", Author = "George", Published = "1949", 
                list(PartOne = c(1:8), 
                     PartTwo = c(1:10),
                     PartThree = c(1:6),
                     PartFour = "Newspeak"))
my.book
str(my.book)

#subsetting the list using [] for first hieararcy, and [[]] for second hieararcy
my.book[1:2]
my.book[4]
my.book[[4]]
my.book[[4]][[2]]

```

#Relational Operator
```{r}
#Relational Operator == similarity != disimilarity < >  <= >=
3 == 3
"cat" == "cat"
"cat" != "rat"
7 > 9
7 < 9
7<= 9

#Logical Operator and "&"  or "|" not "!"
w <- 9

(w > 1 | (w < 12)) # TRUE
(w < 1 | (w < 3)) #FALSE
(w < 12) & (w >6) #TRUE
(w < 6) & (w >6) #FALSE
!(4 < 3) #TRUE

#it also can be used for vector

```

#If and else statement
```{r}

#If and else statement


num <- -3
if(num < 0){
  print("your number is negative")
}

v <- 8
if(v < 0 ){
  v <- v * -1
  print(" I made your object positive")
} else {
  print("your object was already postivite, I did nothing")
}

# else if statement more than two cases

num <- 2
if(num >= 1 & num < 60){
  print("Rotten!")
} else if(num >= 60 & num < 75){
  print("certified fresh")
} else {
  print("please input a number between 1 and 100")
}

```

note : 
1.  A condition for an if statement must have only one element that evaluates to a logical (if vector it will be the first value)
2. an if statement only needs one condition to evaluate to TRUE to stop its search

```{r}
z <- c(1, 0, -3, 5)


#the condition has length > 1 and only the first element will be used

if(z<1){
  print("God save the quees")
}


```

```{r}

#"w is less than 7" because if statement only needs one condition to evaluate to TRUE 

w <- 6
if(w < 7){
  print("w is less than 7")
} else if(w == 6){
  print("w is precisely 6")
} else{
  print("w is more than 7")
  
}
```
```{r}
# For loops

# for(value in x){
#   y
# }

title <- c("catch", "me", "if", "you", "can")
for(word in title){
  print(word)
}

```
```{r}
 # Create a vector filled with random normal values
u1 <- rnorm(30)
print("This loop calculates the square of the first 10 elements of vector u1")

# Initialize `usq`
usq <- 0

for(i in 1:10) {
  # i-th element of `u1` squared into `i`-th position of `usq`
  usq[i] <- u1[i]*u1[i]
  print(usq[i])
}

print(i)
```


For statement is for all the value 
While if the condition is TRUE
need minimum two body expression

# Write a while loop
```{r}


# Write a while loop that sums all the numbers from 1 to n 

n <- 10
i <- 1
sum <- 0

while(i <= n){
  sum <- sum + i
  i <- i + 1
  print(sum)
}


#While loop and repeat loop

n <- 12
while(n < 0){
  print(paste("your value equals", n))
  n <- n + 1
}


repeat{
  print(paste("your value equals", n))
  n <- n + 1
  if(n >= 0){
    print("N is a positive number")
    print("the loop will be broken")
    break
  }
}

```

#Function in R 
local environment is when the function inside the function
"return"  functions provide the base mechanisms for defining new functions in the R language.

```{r}

#simple function example

mult12 <- function(x){
  y <- (x*12)
  return(y)
}

mult12(3)


# What are the principles that determine how R looks up values?

# Answer: 
# If a name isn't defined in the function environment, R will look one level up. 
# If it is, even if there is an element with this name outside of the function, R will not use its value.


# What does this function return? Try to make a prediction before you run it.
# Try to explain why that is.

f <- function(x) {
  f <- function(x) {
    f <- function(x) {
      x ^ 2
    }
    f(x) + 1
  }
  f(x) * 2
}

f(10)

# Answer:
# If a function is defined inside another function, R looks inside the current function for a value, 
# then where that function was defined, and so on, all the way up to the global environment.
```
